Object Oriented Shader Composition Using CLOS

### 2018-04-08 els2018-glsl-oop/paper.tex
Update to new ACM stuff.

\documentclass{sig-alternate}
\usepackage[english]{babel}
\usepackage{float}
\usepackage[labelfont=bf,textfont=md]{caption}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usemintedstyle[glsl]{default}
\usemintedstyle[common-lisp]{default}
\newmintinline[code]{text}{}
\bibliographystyle{unsrt}

@@

@@

\setcopyright{rightsretained}
\doi{}
\isbn{}
\conferenceinfo{ELS'18}{April 16--17, 2018, Marbella, Spain}

@@

\numberofauthors{1}
\author{
  \alignauthor
  Nicolas Hafner\\
  \affaddr{Shirakumo.org}\\
  \affaddr{Zürich, Switzerland}\\
  \email{shinmera@tymoon.eu}
}
\date{21st February 2018}

@@

\printccsdesc

\keywords{Common Lisp, GLSL, OpenGL, GPU, CLOS, MOP, Object Orientation}
\newpage

@@

\section{Implementation}\label{section:9}
An implementation of the proposed system can be found at \href{https://github.com/Shirakumo/trial/blob/e37e0dc73085c401e43da58d5098a9cf02167f8f/shader-entity.lisp}{https://github.com/Shirakumo/trial/blob/\\e37e0dc73085c401e43da58d5098a9cf02167f8f/shader-entity.lisp} for the CLOS part, and at \url{https://github.com/Shirakumo/glsl-toolkit} for the merger part. \\

>>>>

\documentclass[format=sigconf]{acmart}
\usepackage[english]{babel}
\usepackage{float}
\usepackage[labelfont=bf,textfont=md]{caption}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usemintedstyle[glsl]{default}
\usemintedstyle[common-lisp]{default}
\newmintinline[code]{text}{}
\bibliographystyle{unsrt}

@@

\setcopyright{rightsretained}
\acmDOI{}
\acmISBN{978-2-9557474-2-1}
\acmConference[ELS'18]{the 11th European Lisp Symposium}{April 16--17 2018}{%
  Marbella, Spain}

@@

\author{Nicolas Hafner}
\affiliation{%
  \institution{Shirakumo.org}
  \city{Zürich}
  \country{Switzerland}
}
\email{shinmera@tymoon.eu}

@@

\keywords{Common Lisp, GLSL, OpenGL, GPU, CLOS, MOP, Object Orientation}

@@

\newpage

@@

\section{Implementation}\label{section:9}
An implementation of the proposed system can be found at \\\href{https://github.com/Shirakumo/trial/blob/e37e0dc73085c401e43da58d5098a9cf02167f8f/shader-entity.lisp}{https://github.com/Shirakumo/trial/blob/\\e37e0dc73085c401e43da58d5098a9cf02167f8f/shader-entity.lisp} \\ for the CLOS part, and at \url{https://github.com/Shirakumo/glsl-toolkit} for the merger part. \\
